Lyman-$\alpha$ photons through rotating outflows

### 2018-09-21 paper/paper.tex
fix little typo

Figure \ref{fig:doppler_shift} summarizes the most important trends
from rhw RT simulations.
In the left side, the six panels correspond to $\tau=10^6$ and a viewing angle of
$\theta =90^{\circ}$, that is, perpendicular to the rotation axis of the
galaxy. 
In every panel the thin black line corresponds to the pure outflow
solution, i.e. without rotation. 
From top to bottom we see the effect of increasing the outflow
velocity, which is the expected increasing asymmetry towards the red
peak.

@@

Addressing the second question we posed in the introduction (\emph{To what
extent is it possible to constrain rotational kinematics from the \lya
emission line?})  we show that the most straightforward approach
is measuring \lya spectra from two different regions of a
galaxy to detect approaching/receeding gas motions
\citep{Prescott14,2018MNRAS.473.3907A}. 
In that case, we also show that the distances between these two peaks 
is four times shorter than the naively expected value of
$2\times\vrot$.  
This difference is produced by the different geometric weights at the
emitting surface.    
Here the semi-analytic model also provides the correct quantitative
insight.

>>>>

Figure \ref{fig:doppler_shift} summarizes the most important trends
from the RT simulations.
In the left side, the six panels correspond to $\tau=10^6$ and a viewing angle of
$\theta =90^{\circ}$, that is, perpendicular to the rotation axis of the
galaxy. 
In every panel the thin black line corresponds to the pure outflow
solution, i.e. without rotation. 
From top to bottom we see the effect of increasing the outflow
velocity, which is the expected increasing asymmetry towards the red
peak.

@@

Addressing the second question we posed in the introduction (\emph{To what
extent is it possible to constrain rotational kinematics from the \lya
emission line?})  we show that the most straightforward approach
is measuring \lya spectra from two different regions of a
galaxy to detect approaching/receding gas motions
\citep{Prescott14,2018MNRAS.473.3907A}. 
In that case, we also show that the distances between these two peaks 
is four times shorter than the naively expected value of
$2\times\vrot$.  
This difference is produced by the different geometric weights at the
emitting surface.    
Here the semi-analytic model also provides the correct quantitative
insight.
